\documentclass{article}
\usepackage{fullpage}
\usepackage[T1]{fontenc}
\usepackage{titling}
\usepackage{graphicx}
\usepackage{enumitem}

\setlength{\droptitle}{-8em}   % This is your set screw
\title{Homework 4}
\date{}

\begin{document}
\maketitle

\begin{enumerate}
  \item If a staff of $4\mathrm{ft}$ casts a shadow $7\mathrm{ft}$ in length,
      what is the height of a tower which casts a shadow of $198\mathrm{ft}$ at
      the same time? \footnote{Transcribed from: {\em The Progressive Higher
      Arithmetic} edited by Daniel Fish. 1878\label{fn:higher}}
  \item A homeowner sells their house at a loss of $20\%$. If the selling
      price was $\$60,000.00$, what was the original price of the home?
  \item There are approximately 7.5 billion people on the planet. Write this
      number in scientific notation.\label{itm:worldpop}
  \item Last year the Maryville College woods was determined to be home to
      250 box turtles. If the box turtle population has increased by 5\%, what is
      the current population?
  \item Three people are working together on a class project. To complete the
      project, they need to purchase glitter, glue, and a blank T-Shirt. Glitter
      costs \$1.75 per container, glue is \$1.25 per bottle, and a blank T-Shirt
      costs \$6.00. How much must each student contribute to purchase the
      supplies?
  \item Floor*Mart offers two containers of orange juice. One is a 64oz
      container which costs \$5.25 and the other is a 32oz container which costs
      \$2.25. Which container of orange juice is the better buy?
  \item If the speed limit on Alcoa Highway is 55 MPH, how long will it take
      to drive from Maryville to Knoxville (A distance of approximately 17
      miles)?
  \item People seem to enjoy speeding on highways, even though this greatly
      increases their risk of an accident. If we drove the distance in the
      previous question at 65 miles per hour, how long would the trip take? How
      much time did we save by risking our lives and the lives of others?
  \item Gross domestic product is the value of goods and services produced by
      a country each year. In 2018, the gross domestic product of the United
      States was \$19 trillion, and the population of the United States was 327
      million people. How much value did each person produce (assuming everyone
      produced the same amount)? \label{itm:uspop}
  \item Given the population estimate of question \ref{itm:worldpop}, and the
      data in question \ref{itm:uspop}, approximately what percent of the world's
      population lives in the United States?
\end{enumerate}

\end{document}
