\documentclass{article}
\usepackage{fullpage}
\usepackage[T1]{fontenc}
\usepackage{titling}
\usepackage{graphicx}
\usepackage{enumitem}

\setlength{\droptitle}{-8em}   % This is your set screw
\title{Exam 3 Review Problems}

\begin{document}
\maketitle
\begin{enumerate}
\item The height of 10 people (in inches) are given below:
    \newline63 64 67 60 70 72 61 68 69 75
    \newline Write the five number summary for this distribution of
        heights.
\item Another group of people were surveyed, and their heights are
    given below:
    \newline58 65 60 63 67 61 62 65 69 68
    \newline Write the five number summary for this distribution of
    heights.

\item Draw box plots of the two groups.  Is one group generally taller
    than the other?

\item Compute the mean and standard deviation of the first group.  Why
    range of heights would 68\% of the population fall into?  

\item Compute the mean and standard deviation of the second group.  Why
    range of heights would 68\% of the population fall into?  

\item In the game of Monopoly, players roll a pair of six sided dice
    to determine how many squares to move.  If they roll ``doubles'',
    which means the same dumber is showing on both dice, they get to
    take a second turn.  What is the probability of rolling doubles?

\item If a Monopoly player rolls doubles three times in a row during
    a single turn, they are sent to jail.  What is the probability of this
    occurring?

\item Draw a histogram which represents a symmetric distribution.

\item Draw a histogram which represents a distribution with left skew.

\item Draw a histogram which represents a distribution with right skew.

\end{enumerate}
\end{document}
