\documentclass{article}
\title{Lecture 6 Proportions and Change}
\author{Robert Lowe}
\date{September 6, 2019}
\usepackage{fullpage}
\usepackage{amsmath}

\begin{document}
\maketitle

\section*{Change According to Proportions}
\subsection*{Direct Proportions}
\begin{itemize}
\item When something increases by a proportion, this is called a direct proportion.
\item Suppose we have a proportion $a:b :: c:d$.  If an increase in $a$ causes a proportional increase in $c$, then $a:b :: c:d$ is a direct proportion.  
\item You must read the nature of a problem to know whether it is increasing and therefore a direct proportion.
\end{itemize}

\subsection*{Inverse Proportions}
\begin{itemize}
\item When something decreases by a proportion, this is called an inverse proportion.
\item Using the letters $a$, $b$, $c$, and $d$ from the previous problem, if an increase in $a$ causes a decrease in $c$, then the corresponding inverse proportion is $a:b :: d:c$.
\item You must read the nature of a problem to know whether it is decreasing and therefore an inverse proportion.
\end{itemize}

\section*{Change According to Percents}
\subsection*{Increasing, Amount, and Markup}
\begin{itemize}
\item Recall the term amount.  $\mathrm{amount} = \mathrm{base} + \mathrm{percentage}$.
\end{itemize}

\subsection*{Decreasing, Difference, Discount}
\begin{itemize}
\item Recall the term difference.  $\mathrm{difference} = \mathrm{base} - \mathrm{percentage}$.
\end{itemize}

\section*{Percentage and Proportion Problems}
\begin{enumerate}
  \item A besieged town, containing 22,400 inhabitants, has provisions to last 3 weeks; how many must be sent away that they may be able to hold out 7 weeks? \footnote{Transcribed from: {\em A Treatise on Arithmetic} by J. H. Smith. 1878 \label{fn:treatise}}
  \item  If 8 workers in 24 days working 10 hours a day can reap 48 acres of wheat, how many acres could 12 workers reap in 20 days of 12 hours each?
  \item If a staff of $4\mathrm{ft}$ casts a shadow $7\mathrm{ft}$ in length, what is the height of a tower which casts a shadow of $198\mathrm{ft}$ at the same time? \footnote{Transcribed from: {\em The Progressive Higher Arithmetic} edited by Daniel Fish. 1878\label{fn:higher}}
  \item A homeowner sells their house at a loss of $20\%$.  If the selling price was 
  $\$60,000.00$, what was the original price of the home?
  \item In the erection of a house I paid twice as much for material as for labor.  Had I paid $6\%$ more for material, and $9\%$ more for labor, my house would have cost $\$1284.00$; what was its cost?\footnotemark[\ref{fn:higher}].
\end{enumerate}
\end{document}
