\documentclass{article}
\title{Probabilities and Games}
\date{November 1, 2019}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{textcomp}
\usepackage{multicol}
\usepackage{fullpage}
\usepackage{ifsym}
\usepackage{epsdice}

\begin{document}
\maketitle

\section{Probability}
\begin{itemize}
    \item Probability is a way to measure the likelihood of a random
        event.
    \item We start with a set of events, $E$.  For instance, for
        rolling a standard six sided die:
        $E=\{\epsdice{1}, \epsdice{2}, \epsdice{3}, \epsdice{4},
        \epsdice{5}, \epsdice{6}\}$

    \item The probability of any event $e$ in $E$ is computed by:
    \[
        P(e) = \dfrac{\textrm{number of occurrences}}
                     {\textrm{number of trials}}
    \]

    \item We often express probabilities as ratios, decimals, or
        percents.
    \item The probability of every event in a set of outcomes is
        called the probability distribution of the set.
    \item If each outcome is equally likely, we call the distribution a uniform
        probability distribution.
    \item The dice example is a uniform distribution, with each number
        having a 1/6 probability of occurring.
    \item The sum of all the probabilities in a distribution is always
        1. Why?
\end{itemize}

\section{The Game of Craps}
\begin{center}
{\Large
\begin{tabular} {c|c|c|c|c|c|c|}
    \multicolumn{1}{c}{} & 
    \multicolumn{1}{c}{\epsdice{1}} & 
    \multicolumn{1}{c}{\epsdice{2}} & 
    \multicolumn{1}{c}{\epsdice{3}} & 
    \multicolumn{1}{c}{\epsdice{4}} &
    \multicolumn{1}{c}{\epsdice{5}} & 
    \multicolumn{1}{c}{\epsdice{6}} \\
    \cline{2-7}
    \epsdice[black]{1} & 2 & 3 & 4 & 5 & 6 & 7\\
    \cline{2-7}
    \epsdice[black]{2} & 3 & 4 & 5 & 6 & 7 & 8\\
    \cline{2-7}
    \epsdice[black]{3} & 4 & 5 & 6 & 7 & 8 & 9\\
    \cline{2-7}
    \epsdice[black]{4} & 5 & 6 & 7 & 8 & 9 & 10\\
    \cline{2-7}
    \epsdice[black]{5} & 6 & 7 & 8 & 9 & 10 & 11\\
    \cline{2-7}
    \epsdice[black]{6} & 7 & 8 & 9 & 10 & 11 & 12\\
    \cline{2-7}
\end{tabular}
}
\end{center}

\begin{itemize}
    \item Craps is played with a pair of dice.
    \item There is a designated shooter who rolls the dice.
    \item The shooter will have one of two outcomes ``Pass'' (win) or
        ``Don't Pass'' (lose).
    \item The other players bet on the outcome. (There are other bets
        in casino play, but we will focus on the simple win/lose outcomes.)
    \item Each round consists of two phases, the come-out roll and the
        point phase.
\end{itemize}

\subsection{Come-Out Roll}
\begin{itemize}
    \item The shooter rolls the dice once.
    \item A roll of 7 or 11 is a ``natural'' and the pass
        line wins.
    \item A roll of 2, 3, or 12 is ``crapping out'' and the don't
        pass line wins.
    \item Any other roll sets the point value.  The dealer marks the
        value of the roll, and then play proceeds to the point phase.
\end{itemize}

\subsection{Point Phase}
\begin{itemize}
    \item The shooter rolls the dice.
    \item If the shooter rolls the point value established in the
        come-out roll (``hit''), the ``pass'' line wins and the round ends.
    \item If the shooter rolls a 7 (``seven-out''), the ``don't pass'' line wins and
        the round ends.
    \item If the shooter rolls any other number, the point phase
        continues and they roll again.
\end{itemize}

\subsection{Exercises}
\begin{enumerate}
    \item What is the probability of rolling a natural?
    \item What is the probability of crapping out?
    \item What is the probability of proceeding to the point phase?
    \item What is the probability of a seven-out?
    \item What is the probability of hitting each of the possible
        point values?
    \item In groups of three, play a few rounds of craps.  Log the
        outcome of each game. Do your observations match your
        predictions?
    \item Do the following names of the craps rolls make sense?
\begin{center}
{\large
\begin{tabular} {l|l|l|l|l|l|l|}
    \multicolumn{1}{c}{} & 
    \multicolumn{1}{c}{\epsdice{1}} & 
    \multicolumn{1}{c}{\epsdice{2}} & 
    \multicolumn{1}{c}{\epsdice{3}} & 
    \multicolumn{1}{c}{\epsdice{4}} &
    \multicolumn{1}{c}{\epsdice{5}} & 
    \multicolumn{1}{c}{\epsdice{6}} \\
    \cline{2-7}
    \epsdice[black]{1} & Snake Eyes &  & &  &  & \\
    \cline{2-7}
    \epsdice[black]{2} & Ace Deuce & Hard Four &  &  &  & \\
    \cline{2-7}
    \epsdice[black]{3} & Easy Four & Fever Five & Hard Six &  &  & \\
    \cline{2-7}
    \epsdice[black]{4} & Fever Five & Easy Six & Natural & Hard Eight &  & \\
    \cline{2-7}
    \epsdice[black]{5} & Easy Six & Natural & Easy Eight & Nina & Hard Ten & \\
    \cline{2-7}
    \epsdice[black]{6} & Natural & Easy Eight & Nina & Easy Ten & Yo-leven & Boxcars or Midnight\\
    \cline{2-7}
\end{tabular}
}
\end{center}
\end{enumerate}
\end{document}
